Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
Reduced paper to 10 pages

% Convert to single table
\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
\begin{equation}
    T\left(r\right) = L-1-r,
\end{equation}
which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
A brightness control transformation with parameter $v$ is defined as
\begin{equation}
    T\left(r,v\right) = r+v.
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

>>>>

% Convert to single table
\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
\begin{equation}
    T\left(r\right) = L-1-r,
\end{equation}
which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
A brightness control transformation with parameter $v$ is defined as
\begin{equation}
    T\left(r,v\right) = r+v.
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Reduced paper to 10 pages

\subsection{Non-Linear Intensity Transformations}
We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier and DGK), if ciphertext multiplication or division is required, the secure protocols in section~\ref{sssec:pheextension} will be used.

\subsubsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
% TODO: IDK HOW TO CITE OUR PCSC PAPER
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

\subsubsection{Power-Law Transformation}
The power-law transformation of a pixel intensity value $x$ is defined as
\begin{equation}
    T\left(x\right) = cx^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.

Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
We can use partial sums of the following series, which relies on the logarithm function.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.

@@

The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.

>>>>

\subsection{Non-Linear Intensity Transformations}
We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
% \subsubsection{Logarithm Transformation}
In order to perform the logarithm transformation under Paillier and DGK, we use the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
% TODO: HOW ABOUT BGV
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

% \subsubsection{Power-Law Transformation}
To apply the power-law transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
We use partial sums of the following series, which relies on the logarithm function.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.

@@

We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}. In describing each test, we let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

Computation of the MSE between the PDT and CDT, PSNR of the CDT, and SSIM(PDT,CDT) was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
